---
title: "For Paper"
author: "Stephanie Eckman"
date: "7/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(janitor)
require(dplyr)

# date for data sets to use
date <- "20210701"

results <- readRDS(paste0("cnts_results", date, ".rds"))
results.long <- readRDS(paste0("cnts_results_long", date, ".rds"))
sampdist <- readRDS(paste0("cnts_sampdist", date, ".rds"))
gss.liss <- readRDS("gss_liss.rds")
coverage <- readRDS(paste0("cnts_coverage", date, ".rds"))
```

# Results mentioned in paper

## Table 1

### Effect of parameters on observed values

```{r t1}
tapply(results$rr.det, results$delta, summary)

# just to make sure they're similar
tapply(results$rr.sto, results$delta, summary)

tapply(results$samp_var.y, results$theta, summary)

tapply(results$Bias.mean.det, results$rho, summary)

# just to make sure they're similar
tapply(results$Bias.mean.sto, results$rho, summary)


r2 <- results %>% 
  mutate(l2 = if_else(lambda == 0, 0, 1))

tapply(r2$icc, r2$l2, summary)
```

## Section 3.1

### Population Cov(Ybar, Ybar_r) across all Y^norm populations

```{r r1}
summary(results$cov.y.yr)
```

## Section 5.1, Table 5

### Spread of relative bias and rr across 2 example populations

``` {r r2}
tapply(sampdist$rbias, sampdist$pm2, summary)
tapply(sampdist$rr, sampdist$pm2, summary)
```

### Width (97.5%ile - 2.5%tile) by lambda and rho

some variation by lambda, very little by rho

``` {r r2again}
check <- results %>%
  mutate(width = rbias1.mean_q975 - rbias1.mean_q025,
         lt = case_when(lambda == 0 & theta == 5 ~ 1,
                        lambda > 0  & theta == 5 ~ 2,
                        lambda == 0 & theta == 20 ~ 10,
                        lambda > 0  & theta == 20 ~ 11)) 
tapply(check$width, check$lambda, summary)
tapply(check$width, check$lt, summary)
```

## Section 5.2

### Population Cov(Y_r, Y_nr) across Y^norm populations

``` {r r3}
summary(results$cov.yr.ynr)

tapply(results$cov.yr.ynr, results$lambda, summary)

results %>%
  dplyr::select(cov.yr.ynr, lambda) %>%
  arrange(cov.yr.ynr)
```

### Coverage rates by method -- Y^norm

``` {r r4}
tapply(coverage$cov, coverage$.varmethod, summary)

tapply(coverage$cov, interaction(coverage$lambda.f, coverage$.varmethod), summary)
```

## Section 6
``` {r r5, rows.print = 25}
# response rates
gss.liss %>%
  select(survey, rr) %>%
  distinct()

gss2 <- readRDS("gss2.rds")
nrow(gss2)
tabyl(gss2, wave2)

liss2 <- readRDS("liss2.rds")
nrow(liss2)
tabyl(liss2, wave2)

tapply(gss.liss$ratio.rep, gss.liss$survey, summary)
tapply(gss.liss$ratio.lin, gss.liss$survey, summary)

print(gss.liss %>%
  select(survey, var2, bias, n, se.lee, se.lin, se.rep, ratio.rep, ratio.lin) %>%
  arrange(survey, ratio.rep), max = 1000)
```